Which ITG Stepcharts are Turniest?

### 2017-03-13 itg/2/paper.tex
write some itg paper

@@

\keywords
in, the, groove

@@

@@

\texttt{~~~~~~~~~~~~~~~~~~~~~~~~ lastFoot :: \hilight{olivegreen}{Bool}, stepsL :: [\hilight{olivegreen}{Bool}], stepsR :: [\hilight{olivegreen}{Bool}] \}} \\

@@

	\texttt{~~~~~~~~~~~~~~~~~~~~ lastFlip = f, stepsL = \hilight{brickred}{[]}, stepsR = \hilight{brickred}{[]}~\}} \\
\texttt{~~~~\hilight{orange}{where}~ns = \hilight{orange}{length}~\$~~~~~~~~~~~~~~stepsL s ++ stepsR s} \\
\texttt{~~~~~~~~~~nx = \hilight{orange}{length}~\$ \hilight{orange}{filter not}~\$ stepsL s ++ stepsR s} \\

@@

\texttt{~~~~~~~~~~\hilight{commentblue}{-{}- as a tiebreaker, flip if the stream is already more jacky than}} \\

@@

\texttt{~~~~~~~~~~\hilight{commentblue}{-{}- record whether we stepped on a matching or opposite L/R arrow here}} \\
\texttt{~~~~~~~~~~addStep ft \hilight{brickred}{L}~steps = ft:steps} \\
\texttt{~~~~~~~~~~addStep ft \hilight{brickred}{R}~steps = (\hilight{orange}{not}~ft):steps} \\

@@

\texttt{~~~~~~~~~~\hilight{commentblue}{-{}- add the (matching? xover?) step to the list corresponding to this foot.}} \\
\texttt{~~~~~~~~~~newLs s = \hilight{orange}{if}~foot \hilight{orange}{then}~addStep foot step \$ stepsL s \hilight{orange}{else}~stepsL s} \\
\texttt{~~~~~~~~~~newRs s = \hilight{orange}{if}~foot \hilight{orange}{then}~stepsR s \hilight{orange}{else}~addStep foot step \$ stepsR s} \\
\texttt{~~~~~~~~~~stream s = s \{ steps = steps s + \hilight{brickred}{1}, lastStep = \hilight{brickred}{Just}~step,} \\
\texttt{~~~~~~~~~~~~~~~~~~~~~~~~ lastFoot = foot, stepsL = newLs s, stepsR = newRs s \} } \\

@@

	\texttt{\hilight{pink}{analyze}~= \hilight{pink}{commitStream}~. \hilight{orange}{foldl}~\hilight{pink}{analyzeStep}~(\hilight{brickred}{S 0 0 0 0}~\hilight{brickred}{Nothing}~\hilight{brickred}{False}~\hilight{brickred}{False}~\hilight{brickred}{False}~\hilight{brickred}{[] []}) } \\

>>>>

In which I deliver on last year's promise of future work.

@@

\keywords
in, the, groove, 2

@@

Right, let's resume right where I left off in my last paper \cite{turniness}, shown in Figure~\ref{fig:you-stutid-fuckass}.
Unlike mainstream conferences, SIGBOVIK doesn't make me waste space repeating all the background material,
and I can just say go read that paper first and get back to me.
It's probably a lot funnier than this one anyway, which is gonna be sort of dry, and really of interest only to other ITG players.

\begin{figure}[h]
	\includegraphics[angle=90,width=0.48\textwidth]{../paper.pdf}
	\caption{(okay twist your head to read this)}
	\label{fig:you-stutid-fuckass}
\end{figure}

@@

\texttt{~~~~~~~~~~~~~~~~~~~~~~~~ lastFoot :: \hilight{olivegreen}{Bool}, stepsLR :: [\hilight{olivegreen}{Bool}] \}} \\

@@

	\texttt{~~~~~~~~~~~~~~~~~~~~ lastFlip = f, stepsLR = \hilight{brickred}{[]}~\}} \\
\texttt{~~~~\hilight{orange}{where}~ns = \hilight{orange}{length}~\$~stepsLR s} \\
\texttt{~~~~~~~~~~nx = \hilight{orange}{length}~\$ \hilight{orange}{filter not}~\$ stepsLR s} \\

@@

\texttt{~~~~~~~~~~\hilight{commentblue}{-{}- as a tiebreaker, flip if the chart is already more jacky than}} \\

@@

\texttt{~~~~~~~~~~\hilight{commentblue}{-{}- record whether we stepped on a matching or crossed-over L/R arrow.}} \\
\texttt{~~~~~~~~~~addStep ft \hilight{brickred}{L}~steps = steps ++ [ft]} \\
\texttt{~~~~~~~~~~addStep ft \hilight{brickred}{R}~steps = steps ++ [\hilight{orange}{not}~ft]} \\

@@

\texttt{~~~~~~~~~~stream s = s \{ steps = steps s + \hilight{brickred}{1}, lastStep = \hilight{brickred}{Just}~step, lastFoot = foot,} \\
\texttt{~~~~~~~~~~~~~~~~~~~~~~~~ stepsLR = addStep foot step \$ stepsLR s \} } \\

@@

	\texttt{\hilight{pink}{analyze}~= \hilight{pink}{commitStream}~. \hilight{orange}{foldl}~\hilight{pink}{analyzeStep}~(\hilight{brickred}{S 0 0 0 0}~\hilight{brickred}{Nothing}~\hilight{brickred}{False}~\hilight{brickred}{False}~\hilight{brickred}{False}~\hilight{brickred}{[]}) } \\
